Model Search in Relational Domains

### 2016-10-23 learning.tex
Section 6 intro paragraph.

\section{Abstract Conflict Analysis}\label{sec:conflict}
Conflict analysis in a SAT solver can be seen as abductive 
reasoning which underapproximates a set of models that do not satisfy a 
formula~\cite{sas12,dhk2013-popl}.  
\Omit {
where a singleton assignment $c$ is replaced by a partial 
assignment that is sufficient to infer $c$.  Thus, a conflict 
analysis is a generalization of an under-approximation of a set of 
countermodels, where a countermodel is a 
set of structures that do not satisfy a formula 
}
Since relational abstract domains have more complex structure than the partial 
assignments domain or interval domain, so finding a generalized reason for 
conflict through UIP computation~\cite{uip} is non-trivial.  We formally 
describe the adaptations of conflict analysis procedure for relational domains. %
\begin{figure}[t]
\vspace*{-10ex} %BAD TRICK
%\caption{An example of Octagon}\label{octagon}
\scalebox{.65}{\import{figures/}{conflict_graph.pspdftex}}
\caption{\label{conflict} Abstract Conflict Graph}
\end{figure}

>>>>

\section{Abstract Conflict Analysis}\label{sec:conflict}

Conflict analysis in a SAT solver can be seen as abductive 
reasoning which underapproximates a set of models that do not satisfy a 
formula~\cite{sas12,dhk2013-popl}.  
\Omit {
where a singleton assignment $c$ is replaced by a partial 
assignment that is sufficient to infer $c$.  Thus, a conflict 
analysis is a generalization of an under-approximation of a set of 
countermodels, where a countermodel is a 
set of structures that do not satisfy a formula 
}
Relational abstract domains have more complex structure than the partial 
assignments domain or interval domain, so finding a generalized reason for 
conflict through UIP computation~\cite{uip} is non-trivial.  To make this paper self-contained, 
we breifly explain the adaptations that have to be made to the conflict analysis procedure for relational domains. %
\begin{figure}[t]
\vspace*{-10ex} %BAD TRICK
%\caption{An example of Octagon}\label{octagon}
\scalebox{.65}{\import{figures/}{conflict_graph.pspdftex}}
\caption{\label{conflict} Abstract Conflict Graph}
\end{figure}
